### 2024-02-21 presentation/departments.tex
WIP

\makeDepartmentInfo{danish}{compute}{dtu_dep_name_logo/tex_compute_uk}{dtu_dep_logo/tex_dtu_compute_a}{dtu_frise/tex_dtu_frise}{DTU Compute}{Institut for Matematik og Computer Science}
\makeDepartmentInfo{english}{compute}{dtu_dep_name_logo/tex_compute_uk}{dtu_dep_logo/tex_dtu_compute_a_uk}{dtu_frise/tex_dtu_frise}{DTU Compute}{Department of Applied Mathematics and Computer Science}

>>>>

\makeDepartmentInfo{danish}{compute}{dtu_dep_name_logo/tex_compute_uk}{dtu_dep_logo/tex_dtu_compute_a}{dtu_frise/tex_dtu_frise}{DTU Compute}{Institut for Matematik og Computer Science}
\makeDepartmentInfo{english}{compute}{dtu_dep_name_logo/tex_compute_uk}{dtu_dep_logo/tex_dtu_compute_a_uk}{dtu_frise/tex_dtu_frise}{}{Department of Applied Mathematics and Computer Science}
